Batch Bayesian Optimization via Multi-objective Acquisition Ensemble for Automated Analog Circuit Design

### 2018-06-06 paper/experiments.tex
"the Bayesian optimization" => "Bayesian optimization"

The operational amplifier~\cite{wang2014enabling} shown in
Figure~\ref{fig:schDAC2014} is used to test the Bayesian optimization algorithms. The circuit is designed
using the 180nm process. It has 10 design parameters, including the lengths
and widths of transistors, the resistance of the resistors and the capacitance of the
capacitors. The circuit is simulated using the commercial HSPICE circuit simulator.

@@

The class-E power amplifier shown in Figure~\ref{fig:schPA} is used to test the Bayesian optimization algorithms. The
circuit is designed using the 180nm process with 12 design parameters, the
circuit is simulated by the commercial HSPICE circuit simulator to get its performances.

>>>>

The operational amplifier~\cite{wang2014enabling} shown in
Figure~\ref{fig:schDAC2014} is used to test Bayesian optimization algorithms. The circuit is designed
using the 180nm process. It has 10 design parameters, including the lengths
and widths of transistors, the resistance of the resistors and the capacitance of the
capacitors. The circuit is simulated using the commercial HSPICE circuit simulator.

@@

The class-E power amplifier shown in Figure~\ref{fig:schPA} is used to test Bayesian optimization algorithms. The
circuit is designed using the 180nm process with 12 design parameters, the
circuit is simulated by the commercial HSPICE circuit simulator to get its performances.

### 2018-06-06 paper/intro.tex
"the Bayesian optimization" => "Bayesian optimization"

In recent years, the Gaussian process (GP)~\cite{GPML} model has been
introduced for the automated design of analog circuits to reduce the
required number of circuit simulations. In~\citet{liu2014gaspad}, GP is combined
with differential evolution algorithm. Recently, the Bayesian optimization
(BO)~\cite{shahriari2016taking} algorithm has also been applied for analog
circuit optimization. In~\citet{lyu2017efficient}, the Bayesian optimization
algorithm is firstly introduced for the single- and multi-objective
optimization of general analog circuits and has shown to be much more efficient
compared with other simulation-based approaches. In~\citet{wang2017efficient},
the Bayesian optimization algorithm is combined with adaptive Monte-Carlo
sampling to optimize the yield of analog circuits and static random-access
memory (SRAM).

The Bayesian optimization algorithm is a well-studied algorithm and has
demonstrated to be promising for the automated design of analog circuits.
However, the standard Bayesian optimization algorithm is sequential. It chooses
only one point at each iteration by optimizing the acquisition function. It is
often desirable to select a batch of points at each iteration. The sequential
property of Bayesian optimization limits its further applications in multi-core computer systems.

The Bayesian optimization algorithm has been extended to enable batch
selection. Some prior works, like the qEI \cite{qEI}, qKG \cite{wu2016parallel}
and parallel predictive entropy search (PPES)~\cite{shah2015parallel}
approaches, consider to search for the optimal batch selection for a specific
acquisition function. These methods usually involve some approximations or
Monte-Carlo sampling, and thus scale poorly as the batch size increases. Other
works, including the simulation matching (SM)~\cite{azimi2010batch} method, the
batch-UCB (BUCB, BLCB for minimization
problems)~\cite{desautels2014parallelizing} method, the parallel UCB with pure
exploration (GP-UCB-PE)~\cite{contal2013parallel} method, and the local
penalization (LP)~\cite{gonzalez2016batch} method, adopted the \emph{greedy}
strategies that select individual points until the batch is filled.

@@

In this paper, we propose to parallelize the Bayesian optimization algorithm
via the Multi-objective ACquisition Ensemble (MACE). The proposed MACE method
exploits the disagreement between different acquisition functions to enable
batch selection. At each iteration, after the GP model is updated, multiple
acquisition functions are selected. We then perform multi-objective
optimization to find the \emph{Pareto front} (PF) of the acquisition functions.
The PF represents the best trade-off between these acquisition functions. When
batch evaluations are possible, we can sample multiple points on the PF to accelerate the optimization.

>>>>

In recent years, the Gaussian process (GP)~\cite{GPML} model has been
introduced for the automated design of analog circuits to reduce the
required number of circuit simulations. In~\citet{liu2014gaspad}, GP is combined
with differential evolution algorithm. Recently, Bayesian optimization
(BO)~\cite{shahriari2016taking} algorithm has also been applied for analog
circuit optimization. In~\citet{lyu2017efficient}, Bayesian optimization
algorithm is firstly introduced for the single- and multi-objective
optimization of general analog circuits and has shown to be much more efficient
compared with other simulation-based approaches. In~\citet{wang2017efficient},
Bayesian optimization algorithm is combined with adaptive Monte-Carlo
sampling to optimize the yield of analog circuits and static random-access
memory (SRAM).

Bayesian optimization algorithm is a well-studied algorithm and has
demonstrated to be promising for the automated design of analog circuits.
However, the standard Bayesian optimization algorithm is sequential. It chooses
only one point at each iteration by optimizing the acquisition function. It is
often desirable to select a batch of points at each iteration. The sequential
property of Bayesian optimization limits its further applications in multi-core computer systems.

Bayesian optimization algorithm has been extended to enable batch
selection. Some prior works, like the qEI \cite{qEI}, qKG \cite{wu2016parallel}
and parallel predictive entropy search (PPES)~\cite{shah2015parallel}
approaches, consider to search for the optimal batch selection for a specific
acquisition function. These methods usually involve some approximations or
Monte-Carlo sampling, and thus scale poorly as the batch size increases. Other
works, including the simulation matching (SM)~\cite{azimi2010batch} method, the
batch-UCB (BUCB, BLCB for minimization
problems)~\cite{desautels2014parallelizing} method, the parallel UCB with pure
exploration (GP-UCB-PE)~\cite{contal2013parallel} method, and the local
penalization (LP)~\cite{gonzalez2016batch} method, adopted the \emph{greedy}
strategies that select individual points until the batch is filled.

@@

In this paper, we propose to parallelize Bayesian optimization algorithm
via the Multi-objective ACquisition Ensemble (MACE). The proposed MACE method
exploits the disagreement between different acquisition functions to enable
batch selection. At each iteration, after the GP model is updated, multiple
acquisition functions are selected. We then perform multi-objective
optimization to find the \emph{Pareto front} (PF) of the acquisition functions.
The PF represents the best trade-off between these acquisition functions. When
batch evaluations are possible, we can sample multiple points on the PF to accelerate the optimization.
